---
output: rmarkdown::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r init,echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

imagerExtra provides several advanced functions for image processing.

imagerExtra have four functions: EqualizePiecewise, BalanceSimplest, SPE, and DenoiseDCT.


EqualizePiecewise and BalanceSimplest enhance contrast of image.
```{r, message = FALSE}
library(imagerExtra)
g <- grayscale(boats)
layout(matrix(1:4, 2, 2, byrow = TRUE))
plot(boats, main = "Original")
plot(g, main = "Monochrome")
EqualizePiecewise(g, 100) %>% plot(main = "EqualizePiecewise")
BalanceSimplest(g, 1, 1) %>% plot(main = "BalanceSimplest")
```


SPE corrects inhomogeneous background of image.
Note that SPE take a lot of time because of the inefficient implementation of 2D DCT.
```{r, fig.width=7, fig.height=5}
layout(matrix(1:2, 1, 2))
plot(g, main = "Monochrome")
SPE(g, 0.1) %>% plot(main = "SPE")
```


DenoiseDCT denoises noise of image.
```{r}
layout(matrix(1:4, 2, 2, byrow = TRUE))
noisy <- g + imnoise(sd = 0.1, dim = dim(g))
plot(g, main = "Before Adding Noise")
plot(noisy, main = "After Adding Noise")
DenoiseDCT(noisy, sdn = 0.1, flag_dct16x16 = FALSE) %>% plot(main = "Denoised (8x8)")
DenoiseDCT(noisy, sdn = 0.1, flag_dct16x16 = TRUE) %>% plot(main = "Denoised (16x16)")
```


I'm going to add functions.

If you have an idea, let me know by making a issue at [github](https://github.com/ShotaOchi/imagerExtra/issues).




