---
title: "Bug Fixes of BalanceSimplest() and EqualizePiecewise()"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50)) 
```

BalanceSimplest() and EqualizePiecewise() had bugs.

The bug of BalanceSimplest() is shown below.

```{r, error=TRUE}
library(imagerExtra)
g <- grayscale(boats)
BalanceSimplest(g, 0, 1)
```

This is because I forgot index of vector started with 1 in R.

When sleft = 0, BalanceSimplest try to use 0th element of a vector.

BalanceSimplest should use 1st element of a vector when sleft = 0.

The bug of EqualizePiecewise() is shown below.
```{r}
EqualizePiecewise(g, 21850)
```

This is because of integer overflow.

We can reproduce the integer overflow as below.
```{r}
library(Rcpp)
sourceCpp(code = "
  #include <Rcpp.h>
  //[[Rcpp::export]]
  double test(int n, int m, int i) {
    double out = (double)(n * i) / (double)(m + 1); 
    return out;
  }
")
test(10000,1000000, as.integer(3*10^5))
```

We can avoid the overflow as below.
```{r}
sourceCpp(code = "
  #include <Rcpp.h>
  //[[Rcpp::export]]
  double test(int n, int m, int i) {
    double out = (double)n * i / (double)(m + 1); 
    return out;
  }
")
test(10000,1000000, as.integer(3*10^5))
10000 * as.integer(3*10^5) / (1000000 + 1)
```

I fixed the bugs.

Please confirm the bugs were fixed.
```{r, eval=FALSE}
library(devtools)
install_github("ShotaOchi/imagerExtra")
g <- grayscale(boats)
BalanceSimplest(g, 0, 1)
EqualizePiecewise(g, 21850)
```