---
title: "Change of Error Handling"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

I changed the way of error handling.

The functions of imagerExtra returned warning message and NULL value when we input invalid arguments.

Now the functions of imagerExtra returns error message when we input invalid arguments.

This is better because invalid arguments cause errors rather than warnings.

That's why I changed the way of error handling.

You can confirm it by the code below.

```{r, error = TRUE}
library(devtools)
install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
SPE(boats)
```{r}