---
title: "Chan-Vese Segmentation"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

Chan-Vese segmentation is a region-based segmentation algorithm.

Region-based segmentation algorithm can extract objects whose pixesl values are not homogeneous.

I implemented Chan-Vese semgmentation (SegmentCV).

We can use the function as shown below.

```{r, fig.height = 5}
devtools::install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
g <- grayscale(dogs)
layout(matrix(1:2, 1, 2))
plot(g, main = "Original")
b <- SegmentCV(g, lambda2 = 15) %>% plot(main = "Binarized")
```

We can see the belly of the dog was extracted.

It's difficult to extract the belly if we use histogram-based segmentation.

Red curve means boundary of extracted object.

```{r, fig.height = 7}
layout(matrix(1:4, 2, 2))
plot(g, main = "A variant of Otsu"); highlight(threshold(g))
plot(g, main = "Fuzzy Entropy"); highlight(ThresholdFuzzy(g))
plot(g, main = "Iterative Triclass"); highlight(ThresholdTriclass(g))
plot(g, main = "Chan-Vese"); highlight(b) 
```