---
title: "Fast Discrete Cosine Transformation"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

Discrete cosine transform (DCT) is an important tool in the field of image processing.

DCT transforms a signal into the frequencies.

Many of the signal informations are transformed into low frequencies.

Thus, DCT is suitable for frequency filter. 

This is the distionction of DCT. 

I implemented two dimensional discrete cosine transform (DCT2D) and two dimensional inverse discrete cosine transform (IDCT2D).

You can confirm it by the code below.

```{r, error = TRUE}
library(devtools)
install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
layout(matrix(1:2, 1, 2))
g <- grayscale(boats) %>% plot(main = "Original")
gg <- DCT2D(g) %>% IDCT2D() %>% plot(main = "Retransformed")
mean((g - gg)^2)
```{r}
