---
title: "Fuzzy Entropy Image Segmentation"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

Automatic thresholding is important for machine vision.

Otsu's method is a novel algorithm and widely used for machine vision.

However, Otsu's method is not suitable for some cases.

Fuzzy entropy image segmentation can be an alternative in such cases.

I implemented fuzzy entropy image segmentation (ThresholdFuzzy) by following [1].

You can confirm it by the code below.

```{r}
library(devtools)
install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
a <- load.image("http://gahag.net/img/201604/21s/gahag-0078436493-1.jpg") %>% grayscale()
layout(matrix(1:4, 2, 2))
plot(a, main = "Original")
threshold(a) %>% plot(main = "A Variant of Otsu")
ThresholdTriclass(a) %>% plot(main = "Iterative Triclass")
ThresholdFuzzy(a) %>% plot(main = "Fuzzy Entropy")
```

Note that ThresholdFuzzy uses a particle swarm optimization algorithm becase exaustive search is time consuming.

That's why ThresholdFuzzy returns different value every time.

Let's confirm it.

```{r, fig.width=5, fig.height=5}
test <- sapply(1:100, function(x) ThresholdFuzzy(a, returnvalue = TRUE))
hist(test)
````

You can reduce the variance by tuning the parameters of ThresholdFuzzy, although I believe the variance is sufficiently small.

<br />

[1] Linyi Li, Deren Li (2008). Fuzzy entropy image segmentation based on particle swarm optimization. Progress in Natural Science.