---
title: "imagerExtra 1.1.1 released"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

<br />
imagerExtra 1.1.1 was released for a bug fix.

ThresholdTriclass() in imagerExtra 1.1.0 can cause heap buffer overflow.

Heap buffer overflow is exploitable for malicious attack.

This bug was fixed in imagerExtra 1.1.1.

You should update imagerExtra if you use imagerExtra1.1.0.

I'm sorry for exposing you to danger of mallicious attacks.

I promise I'll never expose you to danger of mallicious attack.

I sincerely apologize again.

<br />
<br />

The contents below is a note of how to use AddressSanitizer with R.

The note isn't useful for most users of imagerExtra.

However, it's useful for developers of R packages who aren't familiar with memory error detector.

Of course all important things are written in "Writing R Extentions".

However, it can be overwhelming for R users who aren't familiar with C/C++ compiler.

Moreover, it's hard to find websites that explain how to use memory error detector with R.

I found only one website (its URL is below). 

https://francoismichonneau.net/2014/03/how-to-do-ubsan-tests-r-package/

That's why I leave the note of how to use AddressSanitizer with R.

I hope the note will help someone suffered from memory error.

<br />

***

<br />

## How to use memory error detector with R

We must build R from source to use AddressSanitizer with R.

We can use AddressSanitizer with R after building R.

You should uninstall R before building R if you installed R.

You don't have to uninstall R if you know which commands can cause a problem.

I recommend you to work on Linux.

I was on Ubuntu 18.04 (WSL).

Note that I don't recommend you to use WSL because working with WSL is a little painful for me.

### 1. install required packages 

We must install required packages.

In my case, the packages listed below was required.

you can install these packages by "sudo apt install" if you are on Ubuntu.

* build-essential
* clang
* libcairo2-dev
* libxt-dev
* pandoc 
* qpdf
* texinfo
* texlive-fonts-extra
* valgrind
* subversion
* xorg-dev 
* libreadline-dev
* default-jre 
* default-jdk
* libbz2-dev
* liblzma-dev
* libcurl4-openssl-dev
* libicu-dev
* libfftw3-dev 
* libx11-dev 
* libtiff-dev
* libjpeg-dev

Note that required packages differ depending on R packages.

However, you don't have to be afraid.

You can know which packages are required when configuring compilation (Section 2) and checking R packages (Section 4).

You should read all error messages.

The names of the required packages are written in the messages if the required packages are not in your environment.


### 2. Get R source and configure compilation

Get R source by using subversion.

```{r, eval = FALSE}
svn co https://svn.r-project.org/R/trunk ~/R-devel
cd ~/R-devel
vim config.site
```

edit 'config.site' as shown below.

```{r, eval = FALSE}
  CC="clang -fsanitize=address,undefined -fno-sanitize=float-divide-by-zero -fno-omit-frame-pointer"
  CXX="clang++ -fsanitize=address,undefined -fno-sanitize=float-divide-by-zero -fno-omit-frame-pointer -frtti"
  CFLAGS="-g -O3 -Wall -pedantic"
  FFLAGS="-g -O2 -mtune=native"
  FCFLAGS="-g -O2 -mtune=native" 
  CXXFLAGS="-g -O3 -Wall -pedantic"
  CXXSTD=-std=gnu++98
  MAIN_LD="clang++ -fsanitize=undefined,address"
  LDFLAGS="-L/usr/local/clang/lib64 -L/usr/local/lib64"
  LIBnn="lib64"
```

Note that you have to uncomment.

Then configure compilation.

```{r, eval = FALSE}
 ./configure --prefix=/opt/R/R-devel --without-recommended-packages
```

If there is any complaint, you should resolve it.

### 3. build R and create Makevars.

Build R and create Makevars.

```{r, eval = FALSE}
 make
 sudo make install
 sudo ln -s  /opt/R/R-devel/bin/R /usr/bin/R
 mkdir ~/.R
 vim ~/.R/Makevars
```

Edit Makevars as below.
```{r, eval = FALSE}
 CC = clang -std=gnu99 -fsanitize=undefined -fno-omit-frame-pointer
 CXX = clang++ -fsanitize=undefined -fno-omit-frame-pointer
```
 
### 4. build and check R package with AddressSanitizer

Now we can check R package with AddressSanitizer! Let's check!

```{r, eval = FALSE}
R CMD build --no-build-vignettes --no-manual imagerExtra
R CMD check  --no-manual --no-build-vignettes --no-vignettes imagerExtra_1.1.1.tar.gz
R CMD check  --no-manual --no-build-vignettes --no-vignettes --as-cran --use-gct imagerExtra_1.1.1.tar.gz
R CMD check  --no-manual --no-build-vignettes --no-vignettes --as-cran --use-valgrind imagerExtra_1.1.1.tar.gz
```

Note that these options listed below are not necessary.

* --no-manual 
* --no-build-vignettes 
* --no-vignettes

Below is also OK.
```{r, eval = FALSE}
R CMD build imagerExtra
R CMD check imagerExtra_1.1.1.tar.gz
R CMD check --as-cran --use-gct imagerExtra_1.1.1.tar.gz
R CMD check --as-cran --use-valgrind imagerExtra_1.1.1.tar.gz
```