---
title: "imagerExtra was removed from CRAN"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

imagerExtra 1.3.1 has two problems.

The R package tessetact is in Suggets field of imagerExtra.

However, tesseract is not used conditionally in imagerExtra 1.3.1.

This is a problem.

To prevent installation failure on Solaris, the following code is used in imagerExtra1.3.1.

```{r, eval = FALSE}
if (Sys.info()["sysname"] != "SunOS")
```

This code violates the following CRAN policy.

> Package authors should make all reasonable efforts to provide cross-platform portable code.

This is another problem.

I solved these problems to use the following code instead of the above code.

```{r, eval = FALSE}
if (requireNamespace("tesseract", quietly = TRUE))
```

The code has been implemented in imagerExtra1.3.2.

I submitted imagerExtra 1.3.2 to CRAN.

A CRAN member will respond within 2 weeks.