---
title: "Multilevel Thresholding"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=7, fig.height=7, dev='jpeg',dev.args=list(quality=50))
```

<br />

Multilevel thresholding is useful to extract several kinds of objects whose pixel values are not close.

I implemented automatic multilevel thresholding function (ThresholdML) by following [1].

You can use the function as shown below.

```{r, fig.height=5}
library(devtools)
install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
a <- load.image("https://images.pexels.com/photos/708513/pexels-photo-708513.jpeg") 
a <- crop.borders(a, 1000, 500) %>% resize(., -20, -20, interpolation_type = 5L)
g <- G(a)
b <- ThresholdML(g, 4)
layout(matrix(1:2, 1, 2))
plot(g, main = "Original")
plot(b, main = "Multilevel")
```

We can see three kinds of balls were extracted.

There are four kinds of balls in the original image, but I don't mind.

The background is annoying. We can remove it.

```{r}
bg <- bucketfill(a, 1, 1, color="black", sigma = .1) %>% grayscale()
bg <- bg != 0
s <- (b + 1) * bg
plot(s)
```

Note that ThresholdML uses an artificial bee colony algorithm.

That's why ThresholdML may return different result each time.

```{r, fig.width=5, fig.height=5}
gg <- boats %>% grayscale()
test1 <- sapply(1:1000, function(x) ThresholdML(gg, 4, returnvalue = TRUE)) %>% t()
boxplot(test1, main = "fast", xlab = "thresholds", ylab = "threshold value")
```

We have two options to reduce the variance of the threshold values.

One is to set thr as "precise".

Another is to set thr as "manual" and tune the parameters.

```{r, fig.width=5, fig.height=5}
test2 <- sapply(1:1000, function(x) ThresholdML(gg, 4, thr = "precise", returnvalue = TRUE)) %>% t()
boxplot(test2, main = "precise", xlab = "thresholds", ylab = "threshold value")
```

```{r, fig.width=5, fig.height=5}
test3 <- sapply(1:1000, function(x) ThresholdML(gg, 4, thr = "manual", sn = 200, mcn=200, limit = 10, intervalnumber = 2000, returnvalue = TRUE)) %>% t()
boxplot(test3, main = "manual", xlab = "thresholds", ylab = "threshold value")
```

You can specify threshold values by setting thr to a numeric vector as shown below.

```{r}
thr <- c(0.15, 0.3, 0.45, 0.6)
m <- ThresholdML(g, thr = thr)
plot(m)
```

<br />

[1] Ming-HuwiHorng (2011). Multilevel thresholding selection based on the artificial bee colony algorithm for image segmentation. Expert Systems with Applications.