---
title: "Optical Character Recgnition with imagerExtra"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
---

<style type="text/css">

body, td {
   font-size: 15px;
}
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, comment=NA, verbose=TRUE, 
                      fig.width=7, fig.height=3, dev='jpeg',dev.args=list(quality=50)) 
```

<br />

We can do optical character recgnition by using the R package tesseract.

ocr function of tesseract works best for images with high contrast, little noise and horizontal text.

Then, how should we extract text from a degraded image?

A way is that we enhance contrast of image and denoise image with imagerExtara before using ocr function.

It's convenient we have a function that is shortcut to ocr function if we adopt the way.

That's why I implemented the functions (OCR and OCR_data) that are shortcuts to ocr function and ocr_data function of tesseract.

You can use them as show below.

```{r} 
library(devtools)
install_github("ShotaOchi/imagerExtra")
library(imagerExtra)
layout(matrix(1:2, 1, 2, byrow=TRUE))
plot(papers, main = "Original")
hello <- DenoiseDCT(papers, 0.01) %>% ThresholdAdaptive(., 0.1, range = c(0,1)) %>% plot(main = "Cleaned")
OCR(hello) %>% cat
OCR_data(hello)
```